---
title: "Climate Change"
author: "Mayumi Alino"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("kableExtra")
library(shiny)
analysis_file <- source("app.R")
```
# Heading 1
## Heading 2
**bold text**
p("paragraph")
_italic_

Introduction Page
As you introduce your small project, you should describe the variables that you've chosen to analyze. In doing so, make clear which measure(s) of CO2 emission you are focusing on. 

Then, you will share at least 5 relevant values of interest. These will likely be calculated using your DPLYR skills, answering questions such as: 

What is the average value of my variable across all the counties (in the current year)?
Where is my variable the highest / lowest?
How much has my variable change over the last N years?
Feel free to calculate and report values that you find relevant. Importantly, you should calculate these values in your app_server.R file, and display them in your user interface using the appropriate method. 

```{r echo=FALSE}
  climate_data
```